The Spatial and Temporal Domains of Modern Ecology

### 2017-12-18 paper/SI.tex
After check of calibration dataset in June last commit and again rebuilding calibration vignette in the current version of master, found data didn't change much. There were a few places in TableS2 in SI where values were of at 2nd or 3rd decimal place. Updated those. Values that went into perturbing results did not change. Updated and re-ran through Figure 1 vignette
Added new observational methods figures to SI, updated all figure references in SI.

\begin{table}[ht]
\captionsetup{width=1\linewidth}
\caption{Estimates of variability calculated from each observer's estimates of the spatial and temporal scales of ecological observations reported within a common set of the 20 papers used for calibration. Variability is expressed as the coefficient of variation (CV; standard deviation divided by mean multiplied by 100) between each observer's overall mean, and as the mean CV of observers' estimates for individual records. }
\vspace{-4 pt}
\begin{center}
\begin{tabular}{rR{1.5cm}R{1.5cm}R{1.5cm}R{1.5cm}R{1.5cm}R{1.5cm}}
\hline
& \multicolumn{3}{c}{\textbf{Spatial}} & \multicolumn{3}{c}{\textbf{Temporal}}\\\cline{2-7}
%Value & Resolution & Extent & \multirow{2}{*}{Actual} & Interval & Duration & Actual Duration \\
Value & Resolution & Extent & Actual Extent & Interval & Duration & Actual Duration \\
\hline
CV of overall mean & 50 & 50 & 75 & 48 & 34 & 109 \\
Mean of record-wise CV & 57 & 41 & 72 & 104 & 64 & 126 \\
\hline
\end{tabular}
\end{center}
\label{default}
\end{table}%

@@

\subsubsection*{Trends in observational methods and scales by year}
\vspace{-10pt}
Figures S1 and S2 respectively show how the frequency of ecological observing methods and the average scale in each dimensions varies by publication year (2004-2014).

\begin{figure}[!ht]
%\begin{wrapfigure}{c}{1\textwidth}
\includegraphics[width=1\textwidth]{figures/stype_by_yr.png}
\vspace{10 pt}
\caption{Trends in percentage of observing methods by year of publication. The coefficient of a weighted (by number of studies in each year) linear regression fit to the annual percentages of observations made with remote sensing (left), field methods (center), and automated sensors (right) is presented at the top of each plot, as well as the regression coefficient of determination and p-value. }
\label{afoto1}
\end{figure}

\begin{figure}[ht]
%\begin{wrapfigure}{c}{1\textwidth}
\center{\includegraphics[width=0.8\textwidth]{figures/dim_by_yr.png}}
\vspace{5 pt}
\caption{Trends in observational scales by year of publication. The coefficient of a weighted (by number of studies in each year) linear regression, fit to the logarithm (base 10) of the mean scale values (calculated for each publication year) for the six assessed dimensions is presented at the top of each plot, as well as the model coefficient of determination and p-value. }
\label{afoto1}
\end{figure}
%\clearpage

\subsubsection*{Choice of bandwidth in kernel density estimation}
\vspace{-10pt}
Figure S3 indicates the effect that varying bandwidth has on the appearance of the kernel density estimates. The smallest bandwidth (0.4) tested (Fig. S3 top) shows that the primary observational concentrations described in the main text are evident, but tend to be devolved into separate concentrations. An example is the oblong concentration of observations that in Fig. 1A (and in the lower left panel in Fig. S3) is bounded on the lower right at monthly to yearly intervals and 100-1000 m$^2$ resolutions and on the upper left by near-daily to monthly observations and 0.1-10 ha resolutions. With the smaller bandwidth this concentration appears as two separate patches (Fig. S3 top left), but with 0.7 bandwidth applied becomes coherent (Fig. S3 middle left).  This increasing separation of points into separate clusters is expected as bandwidth is reduced.  However, this assessment indicates that the choice of bandwidth does not alter the interpretation of the results, as the domains of highest and lowest concentrations remain the same.

\begin{figure}[!ht]
%\begin{wrapfigure}{c}{1\textwidth}
\includegraphics[width=0.9\textwidth]{figures/res_v_extent_ksize2.pdf}
\vspace{10 pt}
\caption{Two-dimensional kernel density estimates of observational densities within the domains defined by sampling interval and spatial resolution (left column) and duration and extent (right column), applied to log-transformed values of each observational dimension. Rows indicate the effects of selecting different bandwidths: 0.4 (top row); 0.7 (middle row); 1 (bottom row). }
\label{afoto1}
\end{figure}

>>>>

\begin{table}[ht]
\captionsetup{width=1\linewidth}
\caption{Estimates of variability calculated from each observer's estimates of the spatial and temporal scales of ecological observations reported within a common set of the 20 papers used for calibration. Variability is expressed as the coefficient of variation (CV; standard deviation divided by mean multiplied by 100) between each observer's overall mean, and as the mean CV of observers' estimates for individual records. }
\vspace{-4 pt}
\begin{center}
\begin{tabular}{rR{1.5cm}R{1.5cm}R{1.5cm}R{1.5cm}R{1.5cm}R{1.5cm}}
\hline
& \multicolumn{3}{c}{\textbf{Spatial}} & \multicolumn{3}{c}{\textbf{Temporal}}\\\cline{2-7}
%Value & Resolution & Extent & \multirow{2}{*}{Actual} & Interval & Duration & Actual Duration \\
Value & Resolution & Extent & Actual Extent & Interval & Duration & Actual Duration \\
\hline
CV of overall mean & 50 & 50 & 78 & 49 & 36 & 109 \\
Mean of record-wise CV & 58 & 41 & 72 & 105 & 64 & 126 \\
\hline
\end{tabular}
\end{center}
\label{default}
\end{table}%

@@

\subsubsection*{The domains of observational methods}
\vspace{-10pt}

Fig. \ref{obshists} details the distributions of observations by method along the four primary dimensions, while Fig. \ref{obskde} reveals the densities of observations by method within the dimensional juxtapositions shown in Fig. 2 in the main text.

\begin{figure}[!ht]
%\begin{wrapfigure}{c}{1\textwidth}
\includegraphics[width=1\textwidth]{../vignettes/figures/fig1s.png}
\vspace{-20 pt}
\caption{Histograms of the resolution, extent, interval, and duration of observational scales, shown for all observational methods (top row) and for the four main observational methods (rows 2-5). Bars represent the average percentages for each bin realized after 1000 perturbed resamples, while grey bars indicate the 95\% confidence interval. Bar widths for interval and duration indicate differences in scale between x-axis labels. }
\label{obshists}
\end{figure}

\begin{figure}[!ht]
%\begin{wrapfigure}{c}{1\textwidth}
\includegraphics[width=1\textwidth]{../vignettes/figures/fig2s.png}
\vspace{-20 pt}
\caption{Kernel density estimates across all observational types (top row) and for each of the four primary observational types (rows 2-5). Density estimates for resolution (x axis) versus interval (y axis) are presented in the first column, duration (x) versus interval (y) in the second column, resolution (x) versus extent (y) in the third column, and duration (x) versus extent (y) in the fourth column. Density estimates were applied to the log-transformed values of each observational dimension, and were rescaled to represent percentages. The grey shaded areas represent physically impossible domains (e.g. intervals greater than duration).}
\label{obskde}
\end{figure}

\subsubsection*{Trends in observational methods and scales by year}
\vspace{-10pt}
Figures \ref{type_by_yr} and \ref{sc_by_yr} respectively show how the frequency of ecological observing methods and the average scale in each dimensions varies by publication year (2004-2014).

\begin{figure}[!ht]
%\begin{wrapfigure}{c}{1\textwidth}
\includegraphics[width=1\textwidth]{figures/stype_by_yr.png}
\vspace{10 pt}
\caption{Trends in percentage of observing methods by year of publication. The coefficient of a weighted (by number of studies in each year) linear regression fit to the annual percentages of observations made with remote sensing (left), field methods (center), and automated sensors (right) is presented at the top of each plot, as well as the regression coefficient of determination and p-value. }
\label{type_by_yr}
\end{figure}

\begin{figure}[ht]
%\begin{wrapfigure}{c}{1\textwidth}
\center{\includegraphics[width=0.8\textwidth]{figures/dim_by_yr.png}}
\vspace{5 pt}
\caption{Trends in observational scales by year of publication. The coefficient of a weighted (by number of studies in each year) linear regression, fit to the logarithm (base 10) of the mean scale values (calculated for each publication year) for the six assessed dimensions is presented at the top of each plot, as well as the model coefficient of determination and p-value. }
\label{sc_by_yr}
\end{figure}
%\clearpage

\subsubsection*{Choice of bandwidth in kernel density estimation}
\vspace{-10pt}
Figure \ref{ksens} indicates the effect that varying bandwidth has on the appearance of the kernel density estimates. The smallest bandwidth (0.4) tested (Fig. \ref{ksens} top) shows that the primary observational concentrations described in the main text are evident, but tend to be devolved into separate concentrations. An example is the oblong concentration of observations that in Fig. 1A (and in the lower left panel in Fig. \ref{ksens}) is bounded on the lower right at monthly to yearly intervals and 100-1000 m$^2$ resolutions and on the upper left by near-daily to monthly observations and 0.1-10 ha resolutions. With the smaller bandwidth this concentration appears as two separate patches (Fig. \ref{ksens} top left), but with 0.7 bandwidth applied becomes coherent (Fig. \ref{ksens} middle left).  This increasing separation of points into separate clusters is expected as bandwidth is reduced.  However, this assessment indicates that the choice of bandwidth does not alter the interpretation of the results, as the domains of highest and lowest concentrations remain the same.

\begin{figure}[!ht]
%\begin{wrapfigure}{c}{1\textwidth}
\includegraphics[width=0.9\textwidth]{../vignettes/figures/res_v_extent_ksize2.png}
\vspace{10 pt}
\caption{Two-dimensional kernel density estimates of observational densities within the domains defined by sampling interval and spatial resolution (left column) and duration and extent (right column), applied to log-transformed values of each observational dimension. Rows indicate the effects of selecting different bandwidths: 0.4 (top row); 0.7 (middle row); 1 (bottom row). }
\label{ksens}
\end{figure}
